Circumnuclear Media and Accretion Rates of Quiescent Supermassive Black Holes

### 2015-04-23 ms.tex
cooling flow

>>>>

Note that in practice when $v_{w}<v_{\rm TI}$, a cooling flow may
develop rather than a true local thermal instability: in the former
case the stagnation radius $\rs$ may move to large radii, greatly
increasing the density in the inner part of the flow, which increases
cooling and creates a large inflow of cold gas towards the center of
the galaxy.  In this paper we do not attempt to distinguish under what
conditions a global cooling flow would develop vs. a local thermal
instability.
